Linear instability underlying synchronous waving of marine grass in flow

### 2014-09-06 Paper/grass.tex
The role of critical Reynolds

A threshold in $\Rey$ for the onset of the instability naturally emerges from the solution of \eqref{Orr-somerfield}. 
The dependence of this critical $\Rey$, and the corresponding fastest growing wavenumber $k$, on the $\delta/H$ and $\hg/H$ is shown in figure \ref{Re_vs_delta}, and compared with experimental observation of the threshold\cite{Ghisal02}.

>>>>

A threshold in $\Rey$ for the onset of the instability naturally emerges from the solution of \eqref{Orr-somerfield}. 
The primary reason for the existence of critical $\Rey$ is the presence of dissipation of flow instability 
due to grass drag. Indeed a calculation undertaken for terrestrial grass shows the suppression of growth rate of instability
due to grass drag\cite{Delangre06}. It is important to notice the absence of a threshold condition in the previous analysis of 
free shear flow with various assumptions about mean flow profile and the role of grass drag\cite{Raupach96,Delangre06}.
The dependence of this critical $\Rey$, and the corresponding fastest growing wavenumber $k$, 
on the $\delta/H$ and $\hg/H$ is shown in figure \ref{Re_vs_delta}, and compared with experimental observation of the 
threshold\cite{Ghisal02}.
